Manuscript Preparation

### 2018-05-24 Houston/src/manuscript_preparation.Rmd
asiv21: restructured manuscript_preparation.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
require(markovchain)
require(reshape)
require(survival)
require(caret)
require(e1071)
source("./Houston/src/prepare_violation.R")
source("./Houston/src/roll_over.R")

knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN
```

@@

```{r load data, include=FALSE}
if(!exists("Accidents") | 
   !exists("AssessedViolations") | 
   !exists("Mines")) {
  load("./Houston/data/Accidents.RData")
  load("./Houston/data/AssessedViolations.RData")
  load("./Houston/data/Mines.RData")
  print("raw RData loaded")
}
```

@@

glm.performance <- confusionMatrix(data = glm.result$pred, reference = glm.result$severe, positive = "TRUE")
print(glm.performance)	
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
require(markovchain)
require(reshape)
require(survival)
require(caret)
require(e1071)
knitr::opts_knit$set(root.dir = "~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN

# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/prepare_violation.R")
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/roll_over.R")

# knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN

```

@@

```{r load data, include=FALSE}
source("./Houston/src/prepare_violation.R")
source("./Houston/src/roll_over.R")
if(!exists("Accidents") | 
   !exists("AssessedViolations") | 
   !exists("Mines")) {
  load("./Houston/data/Accidents.RData")
  load("./Houston/data/AssessedViolations.RData")
  load("./Houston/data/Mines.RData")
  print("raw RData loaded")
}
```

@@

glm.performance <- confusionMatrix(data = factor(glm.result$pred), reference = factor(glm.result$severe), positive = "TRUE")
print(glm.performance)	
```
